---
title: "vehicle-silhouette-clustering-r-report"
output: html_document
date: "2025-05-07"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\## Business Value

The business value of this analysis is to identify distinct groups of
vehicles based on their characteristics, which can help in targeted
marketing, product development, and customer segmentation.

This clustering analysis helps to:

-   Understand similarities between vehicle types
-   Reduce dimensionality for better visualization
-   Support automated classification systems based on silhouettes
-   Enhance automotive design, safety analysis, or surveillance-based
    vehicle categorization - Improve customer experience by tailoring
    services to specific vehicle types

\## Problem Statement:

The problem is to cluster vehicles based on their features and evaluate
the quality of the clusters using silhouette analysis.

\## What is a Vehicle Silhouette:

A vehicle silhouette is a two-dimensional representation of a vehicle's
outline, which can be used to analyze its shape and features. In this
analysis, we will use silhouette analysis to evaluate the quality of
clusters formed by different vehicle types based on their
characteristics.

Use Case (Why We Do This)
The silhouettes are analyzed for:

Vehicle classification from surveillance images or camera feeds (security, tolling, traffic monitoring)

Design and shape analysis (e.g., comparing aerodynamic features)

Autonomous driving systems for object recognition and differentiation

This analysis is valuable when you don’t have color, texture, or license plate data — only the shape matters.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to
prevent printing of the R code that generated the plot.
